---
title: "Cristobal - Exercise 15.1"
output: html_document
date: "2023-04-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercises 15.1 

Use R to solve the following.  

1. A machine produces memory sticks of varying lengths, distributed uniformly
between 2 and 12 mm. Memory sticks longer than 10 mm do not meet the
design criterion, and must be scrapped.  
a). Calculate the probability that a memory stick will be scrapped.  
```{r}
p_scrap <- (12-10)/(12-2)
cat("Probability is: ",p_scrap)
```

b). Simulate 50 memory stick lengths and obtain a histogram of the simulated  
values. Calculate the simulated mean and variance. 
```{r}
simulation <- runif(50,2,12)
hist(simulation, main = "Simulation of Lengths", xlab = "millimeters (mm)", col = "maroon", border = "white") 
```

2. Students in an electronic engineering laboratory measure current in using an
ammeter. Due to several random factors, the measurement X follows the pdf
f (x) = 0.025x + b, 2 < x < 6  
(a). Show that, for this to be a genuine probability density, b = 0.15.  
  
```{r}

func <- function(x,b) {out <- .25*x + b}
integ <- integrate(func, 2, 6, b = .15)
integ$value

```

(b). Find the probability that the measurement of the current exceeds 3
```{r}
func <- function(x,b) {out <- .25*x + b}
integ <- integrate(func, lower = 2, upper = 3, b = .15)
prob <- 1 - integ$value

cat("Probability that the current exceeds 3: ", prob)


```




